The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-24 SC-challenge.tex
added some refs for DQ/IQ connection

Modern science and engineering depend on software.
We use citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication.\knnote{Dan: can you support this statement with a citation?} 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
We also need a process to curate and review software.

\knnote{introduce connection to data quality\slash information quality here}
Provenance of research results and data require, among other things, a record of the software used to generate or process that data~\cite{Wilson:2014aa}.
errors in software or variations due to environment~\cite{Soergel:2015aa}

@@

\katznote{Some ideas: \\
\url{https://softwaredatacitation.org/} \\
\url{http://www.software.ac.uk/software-credit}  \\
\url{http://astronomy-software-index.github.io/2015-workshop/} \\
\url{https://geodynamics.org/cig/projects/saga/} \\
maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}

>>>>

Modern science and engineering depend on software.
In fact, a 2009 survey of scientists found that 91\% consider software important or very important to their research~\cite{Hannay:2009wp}.
The scientific community uses citation to acknowledge traditional research results published in archival journals and conferences, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed, shared, and credited is to treat a software release as a publication.\knnote{Dan: can you support this statement with a citation?} 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility~\cite{Sufi:2014en}.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released\slash published software so that it can be cited by others who use it.}
We also need a process to curate and review software.

\knnote{introduce connection to data quality\slash information quality here}
Provenance of research results and data require, among other things, a record of the software used to generate or process that data~\cite{Sandve:2013gh,Wilson:2014aa}.
errors in software or variations due to environment~\cite{Morin:2012hz,Soergel:2015aa}

@@

\katznote{Some ideas: \\
\url{https://softwaredatacitation.org/} \\
\url{http://www.software.ac.uk/software-credit}  \\
\url{http://astronomy-software-index.github.io/2015-workshop/} \\
\url{https://geodynamics.org/cig/projects/saga/} \\
maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group\cite{Allen:2015ub}
